Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering

### 2014-09-13 evaluation.tex
Minor edits, cut to 11 pages.

In order to explore the generality of the architecture for
different monitors, we implemented five different monitors: uninitialized
memory check (UMC), array bounds check (BC), dynamic information flow
tracking (DIFT), instruction-mix profiling (IMP), and LockSet-based race detection (LS).  Uninitialized memory
check seeks to detect loading from
memory locations that are not initialized first. Array bounds check, as
described in Section~\ref{sec:dropping}, is a monitoring scheme that aims to
detect buffer overflows where memory accesses go beyond the boundaries of an
array. We modify the implementation of {\tt malloc} to set base and bound
metadata information. Dynamic information flow tracking is a security
monitoring scheme
which detects when information from untrusted sources is used to affect the
program control flow (i.e., indirect control instructions). For the benchmarks we consider, we mark data read from
files as untrusted. We implemented a multi-bit DIFT scheme which marks
untrusted data with a 32-bit metadata identifier so
that if an error is detected, it is possible to have information about where
the data originated from. Instruction-mix profiling counts the number of ALU,
load, store, and control instructions that are executed. This profiling
information can be useful for performing optimizations or to detect malicious
software \cite{tang-raid14}.
LockSet attempts to detect possible race conditions in multi-threaded programs
by tracking metadata about which locks are protecting shared memory
locations. If a shared memory location is accessed while unprotected
then a race condition may exist. Since we implement the monitor using a
processor core and our dataflow engine was designed to be generally applicable,
the same hardware platform supports all of these monitoring techniques.

>>>>

In order to explore the generality of the architecture for
different monitors, we implemented five different monitors: uninitialized
memory check (UMC), array bounds check (BC), dynamic information flow
tracking (DIFT), instruction-mix profiling (IMP), and LockSet-based race detection (LS).  Uninitialized memory
check seeks to detect loading from
memory locations that are not initialized first. Array bounds check, as
described in Section~\ref{sec:dropping}, is a monitoring scheme that aims to
detect buffer overflows where memory accesses go beyond the boundaries of an
array. We modify the implementation of {\tt malloc} to set base and bound
metadata information. Dynamic information flow tracking is a security
monitoring scheme
which detects when information from untrusted sources is used to affect the
program control flow (i.e., indirect control instructions). For the benchmarks we consider, we mark data read from
files as untrusted. We implemented a multi-bit DIFT scheme which marks
untrusted data with a 32-bit metadata identifier so
that if an error is detected, it is possible to have information about where
the data originated from. Instruction-mix profiling counts the number of ALU,
load, store, and control instructions that are executed. This profiling
information can be useful for performing optimizations or to detect malicious
software \cite{tang-raid14}.
LockSet \cite{eraser-tocs97} attempts to detect possible race conditions in multi-threaded programs
by tracking metadata about which locks are protecting shared memory
locations. If a shared memory location is accessed while unprotected
then a race condition may exist. Since we implement the monitor using a
processor core and our dataflow engine was designed to be generally applicable,
the same hardware platform supports all of these monitoring techniques.

### 2014-09-13 introduction.tex
Minor edits, cut to 11 pages.

% Evaluation
In order to evaluate our approach, we applied it to five different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
% Our experiments show that filtering reduces the average overhead of these
% monitors from 7-18x down to 13-300\%.
% In addition, with partial monitoring, for the monitoring schemes which still
% see average overheads of 300\%, we show that with just 10\% overheads, we can still
% provide 32-82\% of coverage on average. By increasing the
% overhead budget, this coverage rate can be increased. 
These monitors show slowdowns of 1.1-4.3x with the null metadata filtering when
implemented on a multi-core platform.
Our results show that the partial monitoring can still achieve significant
coverage with reduced overheads. For example, for monitors which showed 3-4x
average overheads, slowdown could be reduced to 1.5x while still achieving a
coverage of 43-82\% on average.

>>>>

% Evaluation
In order to evaluate our approach, we applied it to five different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
% Our experiments show that filtering reduces the average overhead of these
% monitors from 7-18x down to 13-300\%.
% In addition, with partial monitoring, for the monitoring schemes which still
% see average overheads of 300\%, we show that with just 10\% overheads, we can still
% provide 32-82\% of coverage on average. By increasing the
% overhead budget, this coverage rate can be increased. 
These monitors show slowdowns of 1.1-4.3x with the null metadata filtering when
implemented on a multi-core platform.
Our results show that the partial monitoring can still achieve significant
coverage with reduced overheads. For example, for the monitors which showed over 3x
average overheads, slowdown could be cut to 1.5x while still achieving a
coverage of 43-82\% on average.

### 2014-09-13 title.tex
Minor edits, cut to 11 pages.

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially for flexible systems that support a range of monitors.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that enables
adjustable overheads through partial monitoring. This allows a trade-off to be
made between monitoring coverage and overhead. This dataflow engine
can also be extended to filter out monitoring operations associated with null
metadata in order to reduce overheads.
% In this paper, we introduce a hardware dataflow tracking engine that can be
% used to filter out unnecessary monitoring and enable adjustable partial monitoring.
% The dataflow engine can identify events with null metadata so that they can
% be filtered out. To further reduce the overhead of monitoring, we propose
% to enable a trade-off between monitoring coverage and overhead by dropping certain
% monitoring operations. For this partial monitoring, the dataflow engine is used
% to track dropped monitoring flows so that false positives can be avoided.
Given this architecture, we investigate how the dropping decisions should be
made for partial monitoring and show that there exist interesting policy
decisions depending on the target application of partial monitoring.
Our experimental results show that overheads can be reduced significantly 
by trading off coverage. For example, with average overheads of 3-4x for full
monitoring range, the proposed architecture can still
achieve 43-82\% coverage when the slowdown is reduced to 1.5x.

>>>>

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially for flexible systems that support a range of monitors.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that enables
adjustable overheads through partial monitoring. This allows a trade-off to be
made between monitoring coverage and overhead. This dataflow engine
can also be extended to filter out monitoring operations associated with null
metadata in order to reduce overheads.
% In this paper, we introduce a hardware dataflow tracking engine that can be
% used to filter out unnecessary monitoring and enable adjustable partial monitoring.
% The dataflow engine can identify events with null metadata so that they can
% be filtered out. To further reduce the overhead of monitoring, we propose
% to enable a trade-off between monitoring coverage and overhead by dropping certain
% monitoring operations. For this partial monitoring, the dataflow engine is used
% to track dropped monitoring flows so that false positives can be avoided.
Given this architecture, we investigate how the dropping decisions should be
made for partial monitoring and show that there exist interesting policy
decisions depending on the target application of partial monitoring.
Our experimental results show that overheads can be reduced significantly 
by trading off coverage. For example, for monitoring techniques with average
overheads of 3-4x, the proposed architecture is able to reduce slowdowns to
1.5x while still achieving 43-82\% average coverage.
